External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms. We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}. The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic} and
CC \cite{crosschannel2016} are listed in Table \ref{tab2}. (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold. One can see that on 9 out of the 15 images, our method achieves the best PSNR values. CC achieves the best PSNR on 3 of the 15 images. It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images. On average, our proposed method has 0.28dB PSNR improvements over [14] and much higher PSNR gains over other competing methods. Fig. 6 shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200. We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image. By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs. More visual comparisons can be found in the supplementary file.

The real noisy images in the second dataset \cite{crosschannel2016} have corresponding ``ground truth" images. On this dataset, we firstly perform comparison on the 15 cropped images used in \cite{crosschannel2016}. The compared method are BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, and Cross-Channel (CC) \cite{crosschannel2016}. The PSNR values are listed in Table \ref{tab2}. As we can see, on most (9 out of the 15) images captured by different cameras and camera settings, our proposed method obtains better PSNR values than the other methods. Noted that, though in \cite{crosschannel2016} a specific model is trained for each camera and camera setting, our proposed general method still gains 0.28dB improvements on PNSR over \cite{crosschannel2016}. We also compare the visual quality of the denoised images by the competing methods. Fig. \ref{fig6} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods. More visual comparisons can be found in the supplementary file. We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TRD are likely to over-smooth the image. By combining the external and internal priors, our proposed method preserves edges and textures better than other methods.

To evaluate the compared methods on more samples, we then perform denoising experiments on the 60 smaller images cropped from the 17 images provided in \cite{crosschannel2016}. The average PSNR results are listed in Table \ref{tab3} (the code of \cite{crosschannel2016} is not available so that it is not compared). The numbers in red color and blue color are the best and second best results, respectively. It can be seen that our proposed method achieves much better PSNR results than the other methods. The improvement of our method over the second best method (TRD) is 1dB. Due to the spacial limitations, the visual comparisions are provided in the supplementary file.

>>>>

As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms. We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}. The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic} and
CC \cite{crosschannel2016} are listed in Table \ref{tab2}. (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold. One can see that on 9 out of the 15 images, our method achieves the best PSNR values. CC achieves the best PSNR on 3 of the 15 images. It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images. On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods. Fig. \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200. We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image. By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs. More visual comparisons can be found in the supplementary file.

We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}. The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available). Again, our proposed method achieves much better PSNR results than the other methods. The improvement of our method over the second best method (TNRD) is about 1dB. Due to the space limitations, the visual comparisons are provided in the supplementary file.
